\chapter*{Introduction}
\label{cha:introduction}

From the coming of Homo habilis about 2.5 million years ago, to the arising of Homo sapiens around 300 thousand years ago, and now with the last years of progression in human knowledge, our species has reached an evolutionary status in which we are more adaptive and more resilient to the natural environment than ever before. Human beings have never stopped trying to go beyond their limits: we invent vehicles, planes, rockets that make it possible to move fast, to fly, or even go beyond the Earth. Nevertheless, our very bodies are still subject to different types of vulnerabilities, such as wounds, injuries, diseases and other physical limitations, as well as appearance, mental and bodily integrity.
The development of modern science and technology has allowed the human race to explore the possibilities of taking control of human evolutionary process, in a sense, which has many interesting and deep implications with respect to body enhancements possibilities, social framework, and the overall paradigm of ethics and philosophy.
Human augmentations: this is the theme of our battle.
In the hypothesis of a not-so-distant future, where the world human society has a structure that very similarly resembles the modern one – wealth and technological divide between western and developing countries, dominant market economy, institutional globalization – the introduction of human enhancing technologies and methods acts on several contexts. The sense of perception of one another is changed, physically at first, but potentially, emotionally as well; enhancing the human potential generates variations on the social fabric; a new market of enhancement products flourishes, with a disruptive potential in various sectors like mobility and healthcare; new regulations are needed to govern the phenomenon, preventing dangerous access divide gaps, dystopian monopolization and implementation of enhancement technologies, societal disorder and segregation…
In this scenario our two sides battle for the domain of one type of human augmentation technology: a team proposes the way of genetic modifications, that of fully being able of programming how our body would work, and of integrating superhuman qualities. The second team proposes the way of cyber augmentations, where the organic is overcome with electromagnetism and material engineering, which opens powerful enhancement possibilities.
