\chapter*{Genetical Modified}
\label{cha:gm}

\section*{Relationship}
\label{sec:gm_relationship}
In the future, humanity will progressively lose its essence due to the continuous evolution and improvement of machines, in the long term, this could lead to machine automation and robotization as the core of everything, placing humans in a marginalized position. For this reason, Genetic Modification is the most suitable solution to keep human beings in a vital place. One of the main points is undoubtedly related to the impact on human relationships, how are the family and, more in general, society structure going to be affected? Nowadays, most of the time, relationships don’t work because people don’t understand each others’ feelings and points of view. One of the reasons behind this issue is the fact that, with the development of more and more advanced technologies, human beings are progressively shifting to experience alternative realities (e.g. virtual reality technology) and at the same time, they are getting far from real relationships, leading them to become increasingly isolated. With genetic modification, human beings will be able to increase their ability to have more empathy and solidarity with each other, this will achieve a deeper connection among them. A good example of this kind of environment is “The Incredibles”, who, although they have superpowers, they manage to keep the family structure and identity as we know it.

\section*{Work}
\label{sec:work}
Genetic Modification affects also the way we have seen the concept of work so far, thanks to it, humans can be smart enough to design and develop robots and systems that will perform all the repetitive tasks. Society, therefore, will encourage people to focus on jobs where creativity and innovation are the key skills and on areas where the performance of robots is quite limited such as design, movies, engineering, etc. Safety at work will considerably improve since professionals from different areas will receive correspondent security measures. For instance, they can be immune to radiation, which can be useful in the medical sector or nuclear sector. 

\section*{Health Care}
\label{sec:health}
The most powerful aspect in which Genetic Modification can affect society is health care. Diseases will no longer be a problem since for each one there will be an available treatment. Not only common diseases we can think about but also remarkable issues affecting the current society. are couples trying to start a family, in which one of the parents has fertility problems, for many of them, nowadays there is not a solution. Also, the process that trans people have to undergo to become the person they feel is very long and complex. Through Genetic Modification this can be easily solved in such a way that these people will feel better about the final result and more confident. 

Probably one of the biggest dangers for society right now is the emergence of antibiotic resistant bacteria. Due to the overuse and misuse of antibiotics, some bacteria are immune to every existent treatment and scientists have not been able to find a solution. Thanks to Genetic Modifications humans will be able to become resistant again. 

In addition to diseases, Genetic Modification is also able to treat accidents in which different organs or body parts are lost or damaged. By bio-reconstruction, the damaged or lost limb can be healed and reinserted in the body. In the worst case, when the mentioned body part cannot be recovered, bio-artificial organs will be used. These bio-artificial organs are done with cells coming from the own patient, so there is no risk of rejection and the feeling will be as the actual one. Finishing with the medical area, therapygenetics will also be covered. This is a science that treats mental diseases and the impact of genetics on them. By exploiting this area and introducing Genetic Modifications, many mental diseases will be easily solved. For instance, genetic illnesses like Alzheimer won’t be a problem anymore because the problem will be solved at the root. As a matter of fact, thanks to genetic modifications, for all the diseases will not only be a cure but will seem like that illness was never taken by the patient. So, putting all together, we will live not only in a healthier society but also happier.

\section*{Ethical boundaries}
\label{sec:ethics}
An essential issue to address when talking about Genetic Modification is ethical boundaries. Human society has always struggled in defining red lines that could find a compromise guaranteeing a peaceful coexistence between everyone. For this reason, Genetic Modification will be subject to regulations. This means that every requested modification - not related to health problems - must be justified, and the reason for the request has to meet requirements depending on different parameters. For example, if someone wants to change his eye color, he will find it easy. However, if he tries to become four meters tall this won’t be achievable since it affects the coexistence. The consequences of each modification have to be clearly pointed out and the individual will have to prove that he is informed about them. Moreover, everyone that wants to perform any change has to be assessed through a psychological test proving that he is in perfect psychological conditions and that he is not being forced by a third person to get that modification. Furthermore, even if someone decides to get a strange modification for his body, that does not mean that that kind of modification will be strange forever. Let’s just think about the social impact of tattoos at the beginning, it was strange for the majority of the population, but nowadays it is a normal thing. Finally, individuals under 18 years old won’t be allowed to get any Genetic Modification except for health purposes. 

\section*{Civil order}
\label{sec:order}
How to maintain civil order in such an unusual scenario? With respect to Genetic Modifications, some measures will be applied, but it has to be taken into account that without cooperation from both sides, they will not be useful. The measures consist of a strong rehabilitation process, where criminals undergo a modification helping them to increase their empathy and therefore become more conscious about society. This process also includes the learning of different skills that help them to reintegrate into society. By doing all this, we are choosing a system focused on reintegration rather than punishment, which in the long-term will tend to reduce criminality. However, since no plan can have 100\% satisfactory results, people with criminal records will have no longer access to Genetic Modifications that can be considered dangerous for society. In a similar way, those in charge of guarantee security will also take advantages of the new advancements. In order to live up to all the different kinds of modifications, the security corps have to go through hard training periods. Those ones, will not only give all the acknowledgment on possible Genetic Modifications of the population but will also coach them on how to handle their powers to make bad guys harmless. So, thanks to Genetic Modification the security corps will be a very well prepared team with powerful Genetic Modifications and the knowledge needed to use them accurately. 

\section*{Population}
\label{sec:population}
The last issue covering is population, which depends on both Genetic Modified humans and Cyborgs. It is not possible to determine the number of people getting each modification, and only some assumptions could be made. First of all, Genetic Modified humans have a life expectancy of around two hundred years. Although the possibility of immortality was an option, it was decided not to exploit it since the disadvantages overcome advantages - the main one is that human life would no longer seem like a normal life, losing its main purpose. Increasing life expectancy could end up with overpopulation. However, we have to take into account that these modifications are only available in developed countries where the real problem is the low birth rate, which leads to a lack of people. But, even if we suppose that at a certain point the problem of overpopulation arises, in the future where these technologies become more accessible, a possible solution is that everyone adopts Genetic Modifications to change the way digestion process takes place in order to obtain more energy and nutrients from less food. This will reduce planet exploitation. 

\section*{Remarks}
\label{sec:gm_remarks}
To sum up, in a world where all the technological improvements lead us to the new digital era of the human race, we can focus ourselves on body enhancements that cannot be reached by the robotization. As a matter of fact, almost every digital task can be reached without the need for implementing machines in our body; we can simply use all the machinery as devices we interact with. By doing so, we are allowed to reach all the benefits described above which will never be reachable by the improved digitalization of the human race. Finally, Genetic Modifications give us the opportunity to improve the creativity, the innovation, and all the other fields that cannot be reached by a simple predefined command executed very fast.
